% EPL master thesis covers template
\documentclass{EPL-master-thesis-covers-EN}

% \documentclass{article}
% \usepackage[utf8]{inputenc}
% \usepackage{float}
% \usepackage{graphicx}
\usepackage{tikz}
\usepackage[demo]{graphicx}
% \usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{enumitem}
\usepackage{amsmath}

\usepackage{graphicx}
\usepackage{float} 
\usepackage{subfigure}



% Please fill in the following boxes
% Title of the thesis
\title{Large-scale data visualization with BH t-SNE, LargeViz, and Umap}

% Subtitle - remove this line if not applicable
%\subtitle{Optional subtitle}

% Name of the student author(s)
\author{Di \textsc{Wu}}
%\secondauthor{Firstname \textsc{Lastname}}		% remove if not applicable
%\thirdauthor{Firstname \textsc{Lastname}}			% remove if not applicable

% Official title of the master degree (copy/paste from list below)
% Master [120] in Biomedical Engineering
% Master [120] in Chemical and Materials Engineering
% Master [120] in Civil Engineering
% Master [120] in Computer Science
% Master [120] in Computer Science and Engineering
% Master [120] in Cybersecurity
% Master [120] in Data Sciences Engineering
% Master [120] in Data Science: Information technology
% Master [120] in Electrical Engineering
% Master [120] in Electro-mechanical Engineering
% Master [120] in Mathematical Engineering
% Master [120] in Mechanical Engineering
% Master [120] in Physical Engineering
% Master [60] in Computer Science
% Specialised master in nanotechnologies
% Specialised master in nuclear engineering
\degreetitle{Master [120] in Data Sciences Engineering}

% Name of the supervisor(s)
\supervisor{John \textsc{Lee}}
\secondsupervisor{Cyril \textsc{De Bodt}}		% remove if not applicable
%\thirdsupervisor{Firstname \textsc{Lastname}}		% remove if not applicable

% Name of the reader(s)
\readerone{Michel \textsc{Verleysen}}
%\readertwo{Firstname \textsc{Lastname}}			% remove if not applicable
%\readerthree{Firstname \textsc{Lastname}}			% remove if not applicable
%\readerfour{Firstname \textsc{Lastname}}			% remove if not applicable
%\readerfive{Firstname \textsc{Lastname}}			% remove if not applicable

% Academic year (update if necessary)
\years{2019--2020}

% Document
\begin{document}

  % Front cover page
  \maketitle
  
\thispagestyle{empty}		% To suppress header and footer on the back of the cover page

\include{chapters/acknowledgments}

\listoftodos

\tableofcontents
\newpage

\include{chapters/intro}
%\include{chapters/background} 
\include{chapters/Algorithms}
\include{chapters/comparison}

% \bookmarksetup{startatroot}
\include{chapters/conclusion}

\begin{thebibliography}{99}  
\bibitem{ref1}Nupur Kumari , Siddarth R, Akash Rupela: High-dimensional Data Visualization at Scale, Computer Vision and Pattern Recognition (CVPR), 2012 IEEE Conference on, IEEE, 2012: 2911-2918.  
\bibitem{ref2}Lowe D G. Distinctive image features from scale-invariant keypoints, International journal of computer vision, 2004, 60(2): 91-110.  
\bibitem{ref3}Philbin J, Chum O, Isard M, et al. Lost in quantization: Improving particular object retrieval in large scale image databases, Computer Vision and Pattern Recognition, 2008. CVPR 2008, IEEE Conference on, IEEE, 2008: 1-8.
\bibitem{ref4}J. A. Lee and M. Verleysen. Quality assessment of dimensionality reduction: Rank-based criteria. Neurocomputing, 72(7):1431–1443, 2009.
\bibitem{ref5}Jian Tang, Jingzhou Liu, Ming Zhang, Qiaozhu Mei. Visualizing Large-scale and High-dimensional Data. 2016, the web conference.
\bibitem{ref6}Freund Y, Dasgupta S, Kabra M, et al. Learning the structure of manifolds using random projections[C]. Advances in Neural Information Processing Systems. 2007: 473-480.

\bibitem{ref7}Goldberg Y, Levy O. word2vec explained: Deriving mikolov et al.’s negative-sampling word-embedding method[J]. arXiv preprint arXiv:1402.3722, 2014.

\bibitem{ref8}C de Bodt, D Mulders, M Verleysen, JA Lee Proc. Extensive assessment of Barnes-Hut t-SNE . ESANN, 135-140, 2018.

\bibitem{ref9}L. Van Der Maaten. Accelerating t-SNE using tree-based algorithms. Journal of Machine Learning Research, 15(1):3221–3245, 2014.

\bibitem{ref10}J. A. Lee and M. Verleysen. Quality assessment of dimensionality reduction: Rank-based criteria. Neurocomputing, 72(7):1431–1443, 2009.

\bibitem{ref11}J. A. Lee, E. Renard, G. Bernard, P. Dupont, and M. Verleysen. Type 1 and 2 mixtures of Kullback-Leibler divergences as cost functions in dimensionality reduction based on similarity preservation. Neurocomputing, 112:92–108, 2013.

\bibitem{ref12}Markus Maier, Matthias Hein, Ulrike von Luxburg. Optimal construction of k-nearest-neighbor graphs for identifying noisy clusters.Theor. Comput. Sci, 2009

\end{thebibliography}

  % Back cover page
  \backcoverpage

\end{document}